---
title: "Homework 3"
output: md_document
date: "2024-02-03"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Working Directory: What is the working directory? What are the best practices for setting and using the working directory?
### The working directory is the directory in the file system where R will look for and save files by default unless otherwise specified. 
1. Always set the working directory at the beginning of your script.
2. Avoid hardcoding paths
3. Consider using the here() package to avoid harcoding paths.
4. Use getwd() to check the current working directory. 
5. Avoid confusion by being aware of where your files are located and where R is looking for them. 


```{r}
name<-"Makhdum Mourad Shah"
ls()
v1 <- c(TRUE, FALSE, TRUE, FALSE, TRUE)
v2 <- c(1L, 2L, 3L, 4L, 5L)
v3 <- c(1.1, 2.2, 3.3, 4.4, 5.5)
v4 <- c("apple", "banana", "watermelon", "mango", "grape")
V <- list(v1, v2, v3, v4)
str(V)
newmatrix <- matrix(data = 1:20, nrow = 4, ncol = 5)
newsequence <- seq(from = 22, to = 44)
newarray <- cbind(newmatrix,newsequence)
element <- v3[3]
d1 <- read.csv("http://hbiostat.org/data/repo/2.20.Framingham.csv")
column_4 <- d1[, 4]
fifth_row <- d1[5, ]

bmi<- d1$bmi
```

## Purpose of this Function:
### The pipe operator allow us to do multiple operations in a concise manner without having to save the intermediate results. 

```{r}

require(dplyr)
# Old way
sum(log(sqrt(select(d1,age)),base=10))

# OG magrittr pipe
d1 %>% 
  pull(age)  %>% 
  sqrt  %>% 
  log(base=10)  %>% 
  sum

d1 %>% 
  lm(sbp ~ dbp, data = .)  # Use the dot if the piped objects needs to go to an input other than the first

d1 %>% 
  split(.$sex) %>%  # Can use the input multiple times
  lapply(function(x){x$age %>% mean})

# New base R pipe
d1 |> 
  pull(age) |> 
  sqrt() |> # Note the parentheses have to be used
  log(base=10) |> 
  sum()

d1 |>  
  lm(sbp ~ dbp, data = _) # Use `_` instead of `.` with new pipe
```

## Prime UVA phone numbers in the form (434) 924-???

```{r}
prime <- function(x){
  ps <- primes::generate_primes(min = 2, max = ceiling(sqrt(x)))
  for(i in ps) if(x%%i == 0) return(FALSE)
  TRUE
}

k <- 0
for(i in 0:9999) {
  phone_number <- 4349240000 + i
  if (prime(phone_number)) {
    k <- k + 1
  }
}
k
```

## List of Prime UVA phone numbers in the form (434) 924-???

```{r}
prime <- function(x) {
  ps <- primes::generate_primes(min = 2, max = ceiling(sqrt(x)))
  for (i in ps) if (x %% i == 0) return(FALSE)
  TRUE
}

k <- 0

for (i in 0:9999) {
  uva_number <- 4349240000 + i
  if (prime(uva_number)) {
    k <- k + 1
    print(paste("(434) 924-", sprintf("%04d", i), " is prime"))
  }
}

```

