---
title: "HW10"
output: md_document
date: "2024-03-01"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
source("https://tgstewart.cloud/mystery.R")
require(dplyr)

## Loading required package: dplyr

## 
## Attaching package: 'dplyr'

## The following objects are masked from 'package:stats':
## 
##     filter, lag

## The following objects are masked from 'package:base':
## 
##     intersect, setdiff, setequal, union

set.seed(223589213)
d1 <- mystery(10000000) |> mutate(vowel = ifelse(is.na(vowel), "zMissing",vowel))
descr::CrossTable(
      d1$location
    , d1$vowel
    , prop.chisq = FALSE
)

##    Cell Contents 
## |-------------------------|
## |                       N | 
## |           N / Row Total | 
## |           N / Col Total | 
## |         N / Table Total | 
## |-------------------------|
## 
## ====================================================================================================
##                d1$vowel
## d1$location           a          e          i          o          u          y   zMissing      Total
## ----------------------------------------------------------------------------------------------------
## 1               1044279     288746     603800     574432     159363       4377          0    2674997
##                   0.390      0.108      0.226      0.215      0.060      0.002      0.000      0.267
##                   0.427      0.124      0.366      0.223      0.256      0.046      0.000           
##                   0.104      0.029      0.060      0.057      0.016      0.000      0.000           
## ----------------------------------------------------------------------------------------------------
## 2               1032774    1315858     758888    1614227     400706      80725          0    5203178
##                   0.198      0.253      0.146      0.310      0.077      0.016      0.000      0.520
##                   0.422      0.563      0.459      0.626      0.643      0.852      0.000           
##                   0.103      0.132      0.076      0.161      0.040      0.008      0.000           
## ----------------------------------------------------------------------------------------------------
## 3                355094     679234     263030     357058      58043       9451          0    1721910
##                   0.206      0.394      0.153      0.207      0.034      0.005      0.000      0.172
##                   0.145      0.291      0.159      0.139      0.093      0.100      0.000           
##                   0.036      0.068      0.026      0.036      0.006      0.001      0.000           
## ----------------------------------------------------------------------------------------------------
## 4                 11866      33965      20019      24810       4598        162          0      95420
##                   0.124      0.356      0.210      0.260      0.048      0.002      0.000      0.010
##                   0.005      0.015      0.012      0.010      0.007      0.002      0.000           
##                   0.001      0.003      0.002      0.002      0.000      0.000      0.000           
## ----------------------------------------------------------------------------------------------------
## 5                  2778      16797       5438       3637        777         32          0      29459
##                   0.094      0.570      0.185      0.123      0.026      0.001      0.000      0.003
##                   0.001      0.007      0.003      0.001      0.001      0.000      0.000           
##                   0.000      0.002      0.001      0.000      0.000      0.000      0.000           
## ----------------------------------------------------------------------------------------------------
## 6                  1018        783        579       2305         43         39          0       4767
##                   0.214      0.164      0.121      0.484      0.009      0.008      0.000      0.000
##                   0.000      0.000      0.000      0.001      0.000      0.000      0.000           
##                   0.000      0.000      0.000      0.000      0.000      0.000      0.000           
## ----------------------------------------------------------------------------------------------------
## 7                    49        198         46        229         21          3          0        546
##                   0.090      0.363      0.084      0.419      0.038      0.005      0.000      0.000
##                   0.000      0.000      0.000      0.000      0.000      0.000      0.000           
##                   0.000      0.000      0.000      0.000      0.000      0.000      0.000           
## ----------------------------------------------------------------------------------------------------
## 8                    10          1         16         40          4          0          0         71
##                   0.141      0.014      0.225      0.563      0.056      0.000      0.000      0.000
##                   0.000      0.000      0.000      0.000      0.000      0.000      0.000           
##                   0.000      0.000      0.000      0.000      0.000      0.000      0.000           
## ----------------------------------------------------------------------------------------------------
## 9                    89          3          0          1          1          0          0         94
##                   0.947      0.032      0.000      0.011      0.011      0.000      0.000      0.000
##                   0.000      0.000      0.000      0.000      0.000      0.000      0.000           
##                   0.000      0.000      0.000      0.000      0.000      0.000      0.000           
## ----------------------------------------------------------------------------------------------------
## 10                    0          0          2          1          0          0          0          3
##                   0.000      0.000      0.667      0.333      0.000      0.000      0.000      0.000
##                   0.000      0.000      0.000      0.000      0.000      0.000      0.000           
##                   0.000      0.000      0.000      0.000      0.000      0.000      0.000           
## ----------------------------------------------------------------------------------------------------
## Inf                   0          0          0          0          0          0     269555     269555
##                   0.000      0.000      0.000      0.000      0.000      0.000      1.000      0.027
##                   0.000      0.000      0.000      0.000      0.000      0.000      1.000           
##                   0.000      0.000      0.000      0.000      0.000      0.000      0.027           
## ----------------------------------------------------------------------------------------------------
## Total           2447957    2335585    1651818    2576740     623556      94789     269555   10000000
##                   0.245      0.234      0.165      0.258      0.062      0.009      0.027           
## ====================================================================================================
```

## 1 If y is the first vowel in a word, what is the probability that it will occur in the third position, like the word why?
From the table, P(3|y) = 0.100.

## 2 Which vowel is most likely to start a word?
From the conditional row probabilities in the table: P(a|1) = 0.39, which is the highest in the row.

## 3 Suppose a randomly selected word's first vowel is in the fourth position. Which vowel is most likely to be first?
From the conditional row probabilities, P(e|4) = 0.356, which is the highest in the row.


## 4 What is the probability that a randomly selected word does not have vowels (a,e,i,o,u, and sometimes y)?
From the margin of the table, P(Inf) = P(Missing vowel) = 0.027

## 5 Are first vowels more likely to be in an odd or even position?
From the margin of the table, P(odd) = 0.4427006






