---
title: "HW 14"
output: md_document
date: "2024-04-18"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 

```{r}

rws <- function(r,k,p_A){

    t(replicate(r,{

        s <- rbinom(2*k-1,1,p_A)

        o <- 1*(sum(s)>=k)

        s_star <- if(o==1){s}else{1-s}

        n <- which(cumsum(s_star) == k)[1]

        c(team=o, games=n)

    }))

}

 
```

## Generate 5000 draws from the world series distribution.



```{r}
draws<-rws(5000,6, 0.45)
head(draws)
```
## With the draws, create the contingency table with number of games as the row variable and winner as the column variable. Include conditional probabilities.

```{r}

library(magrittr)

results_df <- data.frame(number_of_games = draws[, 2], winner = draws[, 1])


contingency_table <- table(results_df$number_of_games, results_df$winner)
conditional_probabilities <- contingency_table %>% proportions() %>%
  addmargins()

print(contingency_table)

print(conditional_probabilities)
```

## Supposing that the world series ends in 2k-1 games, what is the probability that team A will win?
### The probability that Team A wins will be the sum of all the conditional probabilities of the Team A column which is this case is 0.6146.

