---
title: "HW13"
output: md_document
date: "2024-03-26"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## HW 13

1.The following is the contingency table for treatment and recovery that would have resulted had treatment allocation been balanced among gender groups. 

|  | |Recovered | Unrecovered |  | Rate P(recovered!treatment) |                      
| -------------------------- | ----------- | ------------ | ------|------------ | ------|
| All | Active |     0.2   |  0.3  |    0.5  | 0.4 |
|  | Placebo |     0.25    |  0.25    |    0.5  | 0.5 |
| Male | Active |     0.3    |  0.2    |    0.5  | 0.6 |
|  | Placebo |     0.35    |  0.15    |    0.5  | 0.7 |
| Femal | Active |     0.1    |  0.4    |    0.5  | 0.2 |
|  | Placebo |     0.15    |  0.35    |    0.5  | .3 |


2. The same table if twice as many females were likely as males to join the trial. 

|  | |Recovered | Unrecovered |  | Rate P(recovered!treatment) |                      
| -------------------------- | ----------- | ------------ | ------|------------ | ------|
| All | Active |     0.166   |  0.334 |    0.5  | 0.332 |
|  | Placebo |     0.216    |  0.284    |    0.5  | 0.432 |
| Male | Active |     0.3    |  0.2    |    0.5  | 0.6 |
|  | Placebo |     0.35    |  0.15    |    0.5  | 0.7 |
| Femal | Active |     0.1    |  0.4    |    0.5  | 0.2 |
|  | Placebo |     0.15    |  0.35    |    0.5  | .3 |

3. Delta is the treatment effect on the absolute scale, and Rho is the treatment effect on the relative scale. Rho is relative because it is the ratio of the two quantities.

4. From looking at the graph in scenario 1: Δ is -0.1 and ρ is 0.8
 
From looking at the graph in scenario 2: Δ is -0.1 and ρ is 0.76852

Delta(the treatment effect on the absolute scale) stays the same as the proportion of men/women in the trial changes. The expression for Δ is calculated to be = (.2/.5)a + 0.1/0.5 - (.2/.5)a - .15/.5 which will always be equal to 1. Note that "a" refers to the variable alpha. Meanwhile, ρ is calculated to be  ((.2/.5)a + 0.1/0.5) / ((.2/.5)a - .15/.5). 

5. While the data/numbers are identical in the agricultural example, height is not a confounding variable. This means that it is a trait that isn't known at planting and does not effect the variety of the seed. It is a variable on the casual pathway and therefore, it doesn't make sense to adjust/stratify this trait. 


6. ![](ag-dag.svg)

7. 

```{r}

diab <- sample(rep(1:2,times=c(12,13)), 25)
nodiab <- sample(rep(1:2,times=c(38,37)),75)

data.frame(
    diabetes_assignment = c(diab, rep("",50)),
    no_diabetes_assignment = nodiab
)

```


