---
title: "HW5"
output: md_document
date: "2024-02-08"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
big_well <- function(N) 100*rbinom(N, 1, 0.1)
sma_well <- function(N)  10*rbinom(N, 10, 0.1)
set.seed(23459874)
```

## 1. Write code that generates long run proportions for the small well investment opportunity.
```{r}
sma_well(1E6) |>
  table() |>
  proportions()
```
## 2a. Create a figure which visualizes the long-run proportions for the big well investment opportunity. 
```{r}

(big_well(1E6) |>
  table() |>
  proportions())

```

```{r}
barplot(big_well(1E6) |>
  table() |>
  proportions())
```

## 2b.Create a figure which visualizes the long-run proportions for the small well investment opportunity. 
```{r}
barplot(sma_well(1E6) |>
  table() |>
  proportions())
```





## 3. In section 3.9, the author introduces the notation p(E|K). What does K represent?Create an example where the probability of an event is different when K is different.
K denotes our knowledge base and refers to how our knowledge of a certain event can lead to a change in our percieved uncertainty of a situation. For instance, if there is a horse race at 2:30 and we are considering whether a horse will win, if we have prior knowledge as to who the jockey is, who the trainer is, the horse's track record etc, our uncertainty will change. 

## 4. If E denotes an event, what does E^c denote?
If E denotes an event, then E complement denotes th eopposite of that event or any other possible outcomes other than the E. 

## 5. Consider a potentially unfair six-sided die. Let E denote the outcome of a die roll. If P(E is even )=.6, what must P(E is odd ) be? Why?
If P(E is even) is .6 then P(E is odd) will be 0.4. This is because P(E)+P(E^c)=1
